Listed below are the types of charts currently supported in **recharts**. If you are going to try any examples, please make sure you have loaded **recharts** in R:

```{r}
library(recharts)
```

# Line chart

We can use a line chart when `x` is numeric (or date/time) and `y` is numeric. Below is an example of a single curve. We specified `type = 'line'`, without which the plot will be a scatterplot.

```{r}
# an example taken from ?curve
chippy = function(x) sin(cos(x)*exp(-x/2))
x = seq(-8, 7, length = 100)
echart(x = x, y = chippy(x), type = 'line')
```

An example of multiple lines using the `series` argument (the four groups of data have the same correlation coefficient), and an example of a single time series:

```{r}
# see ?anscombe for more info about this dataset
ans = as.matrix(anscombe)
ans = cbind(x = c(ans[, 1:4]), y = c(ans[, 5:8]), group = rep(1:4, each = 11))
ans = ans[order(ans[, 1]), ]
ans = as.data.frame(ans)
str(ans)
echart(ans, ~x, ~y, series = ~group, type = 'line')
echart(y = nhtemp)
```

# Bar chart

When `x` is character or factor, and `y` is numeric or `NULL`, `echart()` will create a bar chart. An example using the `Titanic` data and showing the survival rates in different classes:

```{r}
(classSurv = aggregate(Freq ~ Class + Survived, as.data.frame(Titanic), sum))
echart(classSurv, ~Class, ~Freq, series = ~Survived)
```

An example showing the frequencies of some random numbers cut by 8 intervals:

```{r}
x = cut(rnorm(1000), -4:4)
table(x)
echart(x = x)
```

# Scatterplot

When both `x` and `y` are numeric, `echart()` produces a scatterplot by default. Here is a plot of the `faithful` dataset:

```{r}
echart(faithful, ~eruptions, ~waiting)
```

